Reconciling complexities: for a stronger integration of approaches to complex socio-technical systems

### 2018-05-25 Docs/paper/paper.tex
results

\begin{abstract}
System engineering has developed a mature knowledge on how to design, integrate and manage complex industrial systems, whereas disciplines studying complex systems in nature or society also propose numerous tools for their understanding. Socio-technical systems, that situate at their intersection, could benefit from a higher integration between these. This position paper advocates for such integrated approaches. A bibliometric study through citation networks first illustrates the respective isolation of some of these approaches. We then produce a proof-of-concept of how the transfer of concepts from biology can be useful for the design of complex systems, in the particular case of transportation networks, using a biological network growth model to produce various optimal networks in terms of cost and efficiency. We finally discuss possible disciplinary positioning of such hybrid approaches.
\keywords{System Engineering; Complex Systems Science; Bibliometrics; Bio-inspired Network Design; Integrative Disciplines}
\end{abstract}

@@

% - different types of complexities : systems engineering / even within complex systems
% - but finally treat of the same objects ? debates of top-down/bottom-up

@@

@@

\cite{newman2011complex} for complex systems
% not too specialized, as network science ; agent-based ; dynamical systems ; etc.
% -> good compromise ?

@@

@@

@@

%%%%%%%%%%%%%%
\begin{figure}

	\caption{Example of networks.}
\end{figure}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
\begin{figure}

	\caption{Optimality of simulated networks.}
\end{figure}
%%%%%%%%%%%%%%

@@

% EGI

>>>>

\begin{abstract}
Systems engineering has developed a mature knowledge on how to design, integrate and manage complex industrial systems, whereas disciplines studying complex systems in nature or society also propose numerous tools for their understanding. Socio-technical systems, that situate at their intersection, could benefit from a higher integration between these. This position paper advocates for such integrated approaches. A bibliometric study through citation networks first illustrates the respective isolation of some of these approaches. We then produce a proof-of-concept of how the transfer of concepts from biology can be useful for the design of complex systems, in the particular case of transportation networks, using a biological network growth model to produce various optimal networks in terms of cost and efficiency. We finally discuss possible disciplinary positioning of such hybrid approaches.
\keywords{Systems Engineering; Complex Systems Science; Bibliometrics; Bio-inspired Network Design; Integrative Disciplines}
\end{abstract}

@@

% - socio-technical system at intersection of se/cs
% - different types of complexities : systems engineering / even within complex systems
% - but finally treat of the same objects ? debates of top-down/bottom-up

Socio-technical systems can be understood as the appropriation and use of technical artefacts by social agents, and lie therefore at the intersection of engineered systems and complex social systems. Urban systems are a typical illustration of such systems and of the related issues to design and manage them \cite{portugali2012complexity}.

\paragraph{Systems engineering}

% Incose architecting principles for systems of systems, early works
\cite{maier1998architecting}

% Model-based system engineering
\cite{estefan2007survey}

% international standards
\cite{schneider2013literature}

% current issues examples : coupling mbse and ple
\cite{schafer2017challenges}

\paragraph{Complex systems science}

@@

% complex systems for se ; our paper is in that spirit, illustrating with concrete examples
\cite{sheard2009principles}

% similar with design thinking
\cite{durantin2017disruptive}

@@

\cite{newman2011complex} for complex systems
% not too specialized, as network science ; agent-based ; dynamical systems ; etc.
% -> good compromise ?
% alternative
\cite{stone2000multiagent}

@@

% bridge paper. Note : self-fulfilling, as our work adds a bridge
\cite{hasan2013spatiotemporal}

@@

\cite{langton1989artificial}

% example of cellular automatons
\cite{langton1986studying}

@@

%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.32\linewidth]{figures/bionw_territ6_gamma1_1_bis.png}
	\includegraphics[width=0.32\linewidth]{figures/bionw_territ6_gamma1_2_quart.png}
	\includegraphics[width=0.32\linewidth]{figures/bionw_territ6_gamma1_25_bis.png}\\
	\includegraphics[width=0.32\linewidth]{figures/bionw_territ6_gamma1_3_bis.png}
	\includegraphics[width=0.32\linewidth]{figures/bionw_territ6_gamma1_5.png}
	\includegraphics[width=0.32\linewidth]{figures/bionw_territ6_gamma1_8.png}
	\caption{\textbf{Example of networks.} We show, for a given urban configuration (centers and population density in background color), the networks generated with varying values of the parameter $\gamma$.}
\end{figure}
%%%%%%%%%%%%%%

% Examples (values from netlogo5 - examples urban config)
% gamma = 1.1 (bis)
% observer: "length = 0.46194462288828997"
% observer: "perf = 1.3060253131748516"

% gamma = 1.2 (quart)
% observer: "length = 0.33904251385875966"
% observer: "perf = 1.125244732766119"

% gamma = 1.25 (bis)
% observer: "length = 0.3044382201583243"
% observer: "perf = 1.135368793729363"

% gamma = 1.3 (bis)
% observer: "length = 0.2742468359876043"
%observer: "perf = 1.1384882546283668"

% gamma = 1.5
% observer: "length = 0.26534572051770583"
% observer: "perf = 1.1405973338894875"

% gamma = 1.8
% observer: "length = 0.20788352793069367"
% observer: "perf = 1.308682580064978"

%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=1.2\linewidth]{figures/paretoSpeedLength.png}
	\caption{Pareto evaluation of simulated networks.}
\end{figure}
%%%%%%%%%%%%%%

@@

% EGI
Results obtained in this paper were computed on the vo.complex-system.eu virtual organization of the European Grid Infrastructure ( http://www.egi.eu ). We thank the European Grid Infrastructure and its supporting National Grid Initiatives (France-Grilles in particular) for providing the technical support and infrastructure.
